%========================
% Kevin Esteban Quiceno Cardenas — Backend Resume
%========================

\documentclass[10pt]{article}

\usepackage[letterpaper,left=0.65in,right=0.65in,top=0.55in,bottom=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{microtype}

\pagenumbering{gobble}
\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\linespread{0.96}

\titleformat{\section}{\normalsize\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{4pt}{2pt}

\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt}

\newcommand{\sep}{\;|\;}

\begin{document}

{\Large \textbf{Kevin Esteban Quiceno Cardenas}}

Bradenton, FL \sep (786) 445-3474 \sep
\href{mailto:kevinestebanquicenocardenas@gmail.com}{kevinestebanquicenocardenas@gmail.com}

LinkedIn: \href{https://linkedin.com/in/kevin-esteban-quiceno-0b5b5b333}{linkedin.com/in/kevin-esteban-quiceno-0b5b5b333}
\sep GitHub: \href{https://github.com/KevinEstebanQ}{github.com/KevinEstebanQ}

\textbf{U.S. Work Authorized — No Sponsorship Required}

%========================
\section{Summary}

Computer Engineering graduate from Florida International University (\textbf{Cum Laude, GPA 3.64}) focused on backend and systems engineering. Experience developing backend APIs using \textbf{Python, FastAPI, SQLAlchemy}, containerizing services with \textbf{Docker}, and working with relational databases such as \textbf{PostgreSQL}. Strong foundation in software engineering principles, Linux systems, and distributed application architecture.

%========================
\section{Technical Skills}

\textbf{Languages:}
Python, Java, C, JavaScript, SQL, Bash, HTML, CSS

\textbf{Backend Development:}
FastAPI, REST APIs, SQLAlchemy ORM, Pydantic, JWT Authentication

\textbf{Databases:}
PostgreSQL, SQLite

\textbf{Tools:}
Docker, Docker Compose, Git, GitHub, Linux, VS Code

\textbf{Concepts:}
Data Structures, Algorithms, Operating Systems, Systems Programming, API Design

%========================
\section{Technical Projects}

\textbf{FinanceTrackerService — Backend API} \hfill 2026

Python, FastAPI, SQLAlchemy, PostgreSQL, Docker

\begin{itemize}
\item Developed a RESTful backend service for personal finance tracking using \textbf{FastAPI}.
\item Implemented authentication with password hashing and \textbf{JWT-based access control}.
\item Designed relational data models using \textbf{SQLAlchemy ORM}.
\item Containerized the application using \textbf{Docker Compose} with a PostgreSQL database container.
\end{itemize}

\textbf{ArtaLock Smart Access System — Senior Design Project} \hfill 2025

JavaScript, Electron, Node.js, REST APIs, Jetson Nano

\begin{itemize}
\item Developed the desktop application interface for a facial-recognition access control system.
\item Implemented communication between UI and backend services managing authentication and permissions.
\item \textbf{Led a team of five engineering students} through system integration and final project delivery.
\end{itemize}

\textbf{IBM Cloud Django + SQL Web Application} \hfill 2025

Python, Django, SQL, Cloud Deployment

\begin{itemize}
\item Developed a backend-driven web application using Django and relational databases.
\item Implemented CRUD operations, database integration, and cloud deployment workflows.
\end{itemize}

%========================
\section{Experience}

\textbf{VIZA Migrant-Pro Solutions USA} \hfill Sarasota / Bradenton, FL

IT Support and Web Systems Administration \hfill 2021–Present

\begin{itemize}
\item Managed and maintained the company website and hosting infrastructure.
\item Configured domain management, DNS records, SSL certificates, and server updates.
\item Provided internal IT support including workstation configuration and troubleshooting.
\item Assisted staff with technical tools and digital workflows, improving operational efficiency.
\end{itemize}

%========================
\section{Education}

\textbf{Florida International University} \hfill Miami, FL

Bachelor of Science in Computer Engineering \hfill Dec 2025

Cum Laude \sep GPA: 3.64

Relevant Coursework:
Data Structures, Systems Programming (C), Operating Systems, Embedded Systems, Big Data Analytics

%========================
\section{Professional Development}

Completed the \textbf{Software Development Specialization} and multiple professional courses covering:

Python development, backend systems, database integration, Linux environments, cloud applications, version control (Git), and modern software engineering workflows.

\end{document}